The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-13 analysis/paper/paper.qmd

```{r clean-text}
#| include: false

emu$text_clean <- emu$text_raw |>
  clean_basic()

@@

```{r stop-words}

# TODO replace with cleaning steps including ngram concatenation
# Add cleaned text column with removed stop words
emu$text_clean <- emu$text_clean |>
  str_remove_all(find_meta_stopwords(emu)) |> 
  str_remove_all(urbanism_stopwords(
    add_stopwords = c("emu", "european postgraduate master in urbanism", "tu delft", "ku leuven", "upcs barcelona", "iuav venice", 
                      "space", "spatial", "spaces", "plan", "public", "development"))) |>
  str_remove_all(thesis_stopwords(add_stopwords = c("advisor", "prof", "fig", "ure", "ning")))

# Unnest words and remove words of one and two letters
emu_words <- emu |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>  # remove punctuation, convert to lower-case, separate all words
  anti_join(tidytext::stop_words, by = "word") |>  # remove stop words
  mutate(word = textstem::lemmatize_words(word))  # lemmatise words
```

@@

```{r short-stop-words}
#| include: false

# short_words(emu_words$word, l_word = 3, l_list = 100)

emu_words <- emu_words |>  
  filter(nchar(word) >= 3)  # keep only words that are at least three letters long

@@

bigram_stem_counts <- emu_bigrams |> 
  count(w_1_stem, w_2_stem, sort = TRUE)

bigram_counts
bigram_stem_counts

## Trigrams
emu_trigrams <- emu |> 
  get_ngrams(n = 3, title_col = "title", text_col = "text_raw")

@@

trigram_counts

## Bigram tf-idf
bigram_tf_idf <- emu_bigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

bigram_tf_idf

## Trigram tf-idf
trigram_tf_idf <- emu_trigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

>>>>

@@

```{r pre-process-text}

meta_sw <- find_meta_stopwords(emu)
urbanism_sw <- urbanism_stopwords(
    add_stopwords = c("emu", "european postgraduate master in urbanism", 
                      "european post master in urbanism",
                      "european postmaster in urbanism",
                      "tu delft", "ku leuven", "upc barcelona", "iuav venice"))
thesis_sw <- thesis_stopwords(add_stopwords = c("advisor", "prof", "fig", "ure", "ning"))
ananymisiation_sw <- c("EMAIL_REMOVED", "AUTHOR_REMOVED", "FIRST_NAME_REMOVED", "LAST_NAME_REMOVED") |>
  paste(collapse = "|")
custom_sw <- c("space", "spatial", "spaces", "plan", "public", "development") |>
  (\(.) paste0("\\b", ., "\\b"))() |> 
  paste(collapse = "|")

# Add cleaned text column
emu$text_clean <- emu$text_raw |>
  # Remove white spaces and punctuation, and change text to lower-case
  clean_basic() |>
  # Remove title, subtitle and full title
  str_remove_all(meta_sw) |> 
  # Remove dataset-specific words
  str_remove_all(urbanism_sw) |>
  # Remove thesis-specific words
  str_remove_all(thesis_sw) |> 
  # Remove text included with anonymisation
  str_remove_all(ananymisiation_sw)

# Concatenate ngrams
emu$text_clean <- emu |> 
  c_ngrams(n_max = 3, text_col = "text_clean",
           title_col = "title", min_freq = 20, lemma = TRUE)

  # Words that were not included in ngrams are safe to remove now
emu$text_clean <- emu$text_clean |> 
  str_remove_all(custom_sw)

```{r tokenise}

# TODO Replace title column with ID column

# Unnest tokens and remove words of one and two letters
emu_words <- emu |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>  # remove punctuation, convert to lower-case, separate all words
  anti_join(tidytext::stop_words, by = "word") |>  # remove stop words
  mutate(word = textstem::lemmatize_words(word)) |>  # lemmatise words
  filter(nchar(word) >= 3)  # keep only words that are at least three letters long
```

@@

@@

bigram_tf_idf <- emu_bigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

bigram_tf_idf
```

```{r trigram-tfidf}

emu_trigrams <- emu |> 
  get_ngrams(n = 3, title_col = "title", text_col = "text_raw")

@@

trigram_tf_idf <- emu_trigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))
